Case Study: scRNA-seq (Mouse data, MAST method)

### 2018-03-11 datasets/scrnaseq/scrnaseq-human-scdd.Rmd

```{r, fig.width=4.5, fig.height=3.5, message=FALSE}
rank_scatter(data.frame(rowData(humandata)), 
             pvalue="scdd_p", covariate="meanExp") + 
  ggtitle("scDD, Covariate 1: Mean Expression")
```

```{r, fig.width=10, fig.height=3.2, message=FALSE}
strat_hist(data.frame(rowData(humandata)), 
           pvalue="scdd_p", covariate="meanExp", maxy=35,
           main = "scDD, Covariate 1: Mean Expression") 
```

The mean expression appears to be informative and approximately satisfies the 
assumptions

@@

# properties of method-exclusive discoveries
methods <- c("ashs", "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf",
             "scott-empirical", "scott-theoretical")
mcols(sb2)$ind_covariate <- mcols(sb2)$detection
plotCovariateBoxplots(sb2, alpha=0.1, nsets=6, methods=methods, maxNum=3)+
  ggtitle("scDD, Covariate 2: Detection Rate")

@@

>>>>

```{r, fig.width=4.5, fig.height=3.5, message=FALSE}
rank_scatter(data.frame(rowData(humandata)), 
             pvalue="scdd_p", covariate="meanExp") + 
  ggtitle("scDD, Covariate 1: Mean Nonzero Expression")
```

```{r, fig.width=10, fig.height=3.2, message=FALSE}
strat_hist(data.frame(rowData(humandata)), 
           pvalue="scdd_p", covariate="meanExp", maxy=35,
           main = "scDD, Covariate 1: Mean Nonzero Expression") 
```

The mean nonzero expression appears to be informative and approximately satisfies the 
assumptions

@@

# properties of method-exclusive discoveries
methods <- c("ashs", "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf",
             "scott-empirical", "scott-theoretical")
mcols(sb2)$ind_covariate <- mcols(sb2)$detection
plotCovariateBoxplots(sb2, alpha=0.1, nsets=6, methods=methods, maxNum=3) +
  ggtitle("scDD, Covariate 2: Detection Rate")

@@

```{r, fig.width=8, fig.height=3.5}
covariateHeatmap(sb2, alpha=0.05, covname="ind_covariate") +
  ggtitle("scDD, Covariate 2: Detection Rate")
```

### 2018-03-11 datasets/scrnaseq/scrnaseq-mouse-mast.Rmd

```{r, fig.width=4.5, fig.height=3.5, message=FALSE}
rank_scatter(data.frame(rowData(mousedata)), 
             pvalue="mast_p", covariate="meanExp") + 
  ggtitle("MAST, Covariate 1: Mean Expression")
```

```{r, fig.width=10, fig.height=3.2, message=FALSE}
strat_hist(data.frame(rowData(mousedata)),
           pvalue="mast_p", covariate="meanExp", maxy=16,
           main = "MAST, Covariate 1: Mean Expression")
```

The mean expression appears to be informative and approximately satisfies the 
assumptions

@@

# properties of method-exclusive discoveries
methods <- c("ashs", "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf",
             "scott-empirical", "scott-theoretical")
mcols(sb2)$ind_covariate <- mcols(sb2)$detection
plotCovariateBoxplots(sb2, alpha=0.1, nsets=6, methods=methods, maxNum=3)+
  ggtitle("MAST, Covariate 2: Detection Rate")

>>>>

```{r, fig.width=4.5, fig.height=3.5, message=FALSE}
rank_scatter(data.frame(rowData(mousedata)), 
             pvalue="mast_p", covariate="meanExp") + 
  ggtitle("MAST, Covariate 1: Mean Nonzero Expression")
```

```{r, fig.width=10, fig.height=3.2, message=FALSE}
strat_hist(data.frame(rowData(mousedata)),
           pvalue="mast_p", covariate="meanExp", maxy=16,
           main = "MAST, Covariate 1: Mean Nonzero Expression")
```

The mean nonzero expression appears to be informative and approximately satisfies the 
assumptions

@@

# properties of method-exclusive discoveries
methods <- c("ashs", "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf",
             "scott-empirical", "scott-theoretical")
mcols(sb2)$ind_covariate <- mcols(sb2)$detection
plotCovariateBoxplots(sb2, alpha=0.1, nsets=6, methods=methods, maxNum=3) +
  ggtitle("MAST, Covariate 2: Detection Rate")
